Ground state energy of quantum dots using the coupled cluster method

### 2018-05-15 project_2/article/article.tex
Deltas on second amplitude equation term. Missing four or four to spare?

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}.
		\end{aligned}
		\end{equation}
		The one-electron component does not have any full contractions, while the
		two-electron component produces one contributing integral,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(V_N)\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0} \\
			 	=& \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} \\ &\times\Big(
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\} \\
			 	  &\ +
			 	 	\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 	\Big) \\
			 	=&  \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} 
			 	( \delta_{ap}\delta_{bq}\delta_{js}\delta_{ir}
			 	 -\delta_{aq}\delta_{bp}\delta_{js}\delta_{ir} \\
			     &\ -\delta_{ap}\delta_{bq}\delta_{jr}\delta_{is}
			 	 +\delta_{aq}\delta_{bp}\delta_{jr}\delta_{is}) = \bra{ab}\ket{ij}.
		\end{aligned}
		\end{equation}

>>>>

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}.
		\end{aligned}
		\end{equation}
		The one-electron component does not have any full contractions, while the
		two-electron component produces one contributing integral,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(V_N)\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0} \\
			 	=& \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} \\ &\times\Big(
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c1 a^\dagger_i \c2 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\} \\
			 	  &\ +
			 	 	\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c3 a_b \c4 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 		+
			 		\{ \wick{\c2 a^\dagger_i \c1 a^\dagger_j \c4 a_b \c3 a_a
			 		\c4 a^\dagger_p \c3 a^\dagger_q \c2 a_s \c1 a_r}\}
			 	\Big) \\
			 	=&  \frac{1}{4} \sum_{pqrs} \bra{pq}\ket{rs} 
			 	( \delta_{ap}\delta_{bq}\delta_{js}\delta_{ir}
			 	 -\delta_{aq}\delta_{bp}\delta_{js}\delta_{ir} \\
			     &\ -\delta_{ap}\delta_{bq}\delta_{jr}\delta_{is}
			 	 +\delta_{aq}\delta_{bp}\delta_{jr}\delta_{is}) \\
			 	 =& \bra{ab}\ket{ij} = u^{ab}_{ij}.
		\end{aligned}
		\end{equation}

		Next we would like to evaluate $\bra{\Phi_{ij}^{ab}}(F_N + V_N)T_2\ket{\Phi_0}$. Starting with the 
		term involving the Fock operator $F_N$,
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}}&F_NT_2\ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pq}\sum_{klcd}f_{pq}t_{kl}^{cd} \bra{\Phi_0}
					\{a_i^\dagger a_j^\dagger a_b a_a \}(\{a^\dagger_pa_q \}\{a^\dagger_c a^\dagger_d a_l a_k \})_c \ket{\Phi_0} \\
				=& \frac{1}{4}\sum_{pq}\sum_{klcd}f_{pq} t_{kl}^{cd} \\
				\times \Big(
					&\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c2 a_q \c3 a^\dagger_c \c4 a^\dagger_d \c1 a_l \c5 a_k } \}
				 + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c1 a_q \c3 a^\dagger_c \c4 a^\dagger_d \c2 a_l \c5 a_k } \}	\\
			    + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c2 a_q \c4 a^\dagger_c \c3 a^\dagger_d \c1 a_l \c5 a_k } \}
				 + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c1 a_q \c4 a^\dagger_c \c3 a^\dagger_d \c2 a_l \c5 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c1 a_q \c3 a^\dagger_c \c4 a^\dagger_d \c5 a_l \c2 a_k } \}
		          + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c1 a_q \c4 a^\dagger_c \c3 a^\dagger_d \c5 a_l \c2 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c2 a_q \c3 a^\dagger_c \c4 a^\dagger_d \c5 a_l \c1 a_k } \}
		          + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c5 a^\dagger_p \c2 a_q \c4 a^\dagger_c \c3 a^\dagger_d \c5 a_l \c1 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c3 a^\dagger_p \c5 a_q \c5 a^\dagger_c \c4 a^\dagger_d \c2 a_l \c1 a_k } \}
		     	 + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c3 a^\dagger_p \c5 a_q \c5 a^\dagger_c \c4 a^\dagger_d \c1 a_l \c2 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c4 a^\dagger_p \c5 a_q \c5 a^\dagger_c \c3 a^\dagger_d \c2 a_l \c1 a_k } \}
		          +\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c4 a^\dagger_p \c5 a_q \c5 a^\dagger_c \c3 a^\dagger_d \c1 a_l \c2 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c3 a^\dagger_p \c5 a_q \c4 a^\dagger_c \c5 a^\dagger_d \c1 a_l \c2 a_k } \}
		          +\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c3 a^\dagger_p \c5 a_q \c4 a^\dagger_c \c5 a^\dagger_d \c2 a_l \c1 a_k } \} \\
		        + &\{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c3 a^\dagger_p \c5 a_q \c4 a^\dagger_c \c5 a^\dagger_d \c1 a_l \c2 a_k } \}
		          + \{\wick{\c1 a^\dagger_i \c2 a^\dagger_j \c3 a_b \c4 a_a \c4 a^\dagger_p \c5 a_q \c3 a^\dagger_c \c5 a^\dagger_d \c2 a_l \c1 a_k } \}
				\Big) \\
				=& \sum_{pq}\sum_{klcd}f_{pq} t_{kl}^{cd} \\
				\times&( - \delta_{a c} \delta_{b d} \delta_{i k} \delta_{j q} \delta_{l p} + \delta_{a c} \delta_{b d} \delta_{i l} \delta_{j q} \delta_{k p}  \\
				 \ &+ \delta_{a c} \delta_{b d} \delta_{i q} \delta_{j k} \delta_{l p} - \delta_{a c} \delta_{b d} \delta_{i q} \delta_{j l} \delta_{k p} \\
				 \ &+ \delta_{a c} \delta_{b p} \delta_{d q} \delta_{i k} \delta_{j l} - \delta_{a c} \delta_{b p} \delta_{d q} \delta_{i l} \delta_{j k} \\
				 \ & + \delta_{a d} \delta_{b c} \delta_{i k} \delta_{j q} \delta_{l p} - \delta_{a d} \delta_{b c} \delta_{i l} \delta_{j q} \delta_{k p} \\
				 \ &- \delta_{a d} \delta_{b c} \delta_{i q} \delta_{j k} \delta_{l p} + \delta_{a d} \delta_{b c} \delta_{i q} \delta_{j l} \delta_{k p} \\
				 \ &- \delta_{a d} \delta_{b p} \delta_{c q} \delta_{i k} \delta_{j l} + \delta_{a d} \delta_{b p} \delta_{c q} \delta_{i l} \delta_{j k} \\
				 \ &- \delta_{a p} \delta_{b c} \delta_{d q} \delta_{i k} \delta_{j l} + \delta_{a p} \delta_{b c} \delta_{d q} \delta_{i l} \delta_{j k} \\
				 \ &+ \delta_{a p} \delta_{b d} \delta_{c q} \delta_{i k} \delta_{j l} - \delta_{a p} \delta_{b d} \delta_{c q} \delta_{i l} \delta_{j k}) \\
				 =& (f_{bc}t^{ac}_{ij} - f_{ac}t^{bc}_{ij}) - (f_{jk}t^{ab}_{ik} - f_{ik}t^{ab}_{jk}) \\
				 =& f_{bc}t^{ac}_{ij}P(ab) - f_{kj}t^{ab}_{ik} \\
				 =& u_{cm}^{bm}t_{ij}^{ac}P(ab) + u_{jm}^{mk}t_{ik}^{ab}P(ij)
		\end{aligned}
		\end{equation}		
		Where in the last steps we have consigned the sums by Einstein summation notation.
		We have also only included the two-body part of the fock operator, because we are
		dealing with double excitations (relaxations) only.

		One could of course continue in this manner, employing Wick's general theorem to all
		terms that arises from combining \autoref{eq:normal_order_expansion}
		\autoref{eq:doubles_amplitude_1}, but because this task is quite strenuous, we employ
		the second quantisation library from SymPy instead\footnote{This is also more in the
		spirit of this project, as it is in the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + t^{ac}_{ij} u^{bm}_{cm} P(ab) + t^{ab}_{ik} u^{mk}_{jsm} P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{nm} u^{nm}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 -& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{nm}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 -& t^{ac}_{im} t^{bd}_{jn} u^{nm}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{nm} u^{nm}_{ij}, 
		\end{aligned}
		\end{equation}

		where we recognize the first three terms.
